Bayesian methods for black hole merger parameter estimation with LISA.

### 2019-03-15 paper/paper_PE.tex
Added plots to the paper

\section{Morphology of the signals}
\label{sec:morph}

- Morphology of the response

@@

@@

@@

@@

>>>>

@@

\begin{figure*}
  \centering
  \includegraphics[width=.98\linewidth]{../plots/plot_smbh9_alltdi.pdf}
  \caption{\SM{TODO: rethink the visualization, maybe plot only transfer functions}.}
  \label{fig:tranferSMBHCase9}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=.7\linewidth]{../plots/plot_tdia_hm.pdf}
  \caption{\SM{TODO: make figure smaller, single-column.}}
  \label{fig:FDHMSMBHCase9}
\end{figure*}

@@

\begin{figure*}
  \centering
  \begin{minipage}{.32\linewidth}
      \includegraphics[width=.99\linewidth]{../plots/corner_smbh_case9_hm_tseries_m1m2.png}
   \end{minipage}
   \begin{minipage}{.32\linewidth}
      \includegraphics[width=.99\linewidth]{../plots/corner_smbh_case9_hm_tseries_Dinc.png}
   \end{minipage}
   \begin{minipage}{.32\linewidth}
      \includegraphics[width=.99\linewidth]{../plots/corner_smbh_case9_hm_tseries_tphi.png}
   \end{minipage}
  \caption{.}
  \label{fig:smbhCornerZoomHMCase9}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=.8\linewidth]{../plots/plot_mollweide_tseries.png}
  \caption{.}
  \label{fig:MollweidesmbhTserieshmCase9}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=.8\linewidth]{../plots/corner_smbh_case9_simplelike_ptmcmc_bambi.png}
  \caption{.}
  \label{fig:PEsmbh22hmSimpleLikeCase0}
\end{figure*}

\begin{figure}
  \centering
  \begin{minipage}{.49\linewidth}
  \includegraphics[width=.99\linewidth]{../plots/corner_skydown_smbh_case9_22_ptmcmc_bambi_withdegen.png}
  \end{minipage}
  \begin{minipage}{.49\linewidth}
  \includegraphics[width=.99\linewidth]{../plots/corner_skydown_smbh_case9_simplelike_ptmcmc_bambi_withdegen.png}
  \end{minipage}
  \caption{.}
  \label{fig:Skydownsmbh22hmSimpleLikeCase0}
\end{figure}

@@

\subsection{Signals and transfer functions}
\label{subsec:signaltransferSOBH}

\begin{figure*}
  \centering
  \includegraphics[width=.98\linewidth]{../plots/plot_sobh1_alltdi.pdf}
  \caption{\SM{TODO: rethink the visualization, maybe plot only transfer functions}.}
  \label{fig:PEsmbh22hmCase0}
\end{figure*}
